### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
read again the Che Ming Ko paper, this could indeed be problematic, added a comment
smaller corrections still related to the rms

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

@@

>>>>

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

@@

   % -> http://inspirehep.net/record/1662034 (I think that he is double counting => he should remove the protons and neutrons that have already coalesced into a hyper-triton from the sample. He argues that this is one different time scales which might explain it, ie. the volume for which hyper-triton coalescence happens is just much larger than the one in which deuteron coalescence happens. However, if the two different time-scales are true ? in our approach a much larger volume ? then they should not show so much radial/elliptic flow as they are then formed after decoupling? ==> THIS COULD SOMEHOW DESTROY THE WHOLE STORY.)
